### 2017-11-30 manuscript.rmd
fleshed Evolution of Vertical habitat

Siphonophores are abundant predators in the pelagic realm, ranging from the surface (*Physalia physalis*) to bathypelagic depths (Figure 4, S5) [@mapstone2014global]. While there are some pleustonic (*Physalia*) and benthic (*Rhodaliidae*) siphonophores, the phylogeny suggests the siphonophore MRCA was planktonic, as most extant taxa are. Some interesting questions arise from these facts, including 1) what was the bathymetric niche of the siphonophore MRCA, and 2) how did siphonophore's vertical habitat use of the water columns evolve along the phylogeny. Our results indicate a mesopelagic MRCA, with several convergent transition events to epipelagic and bathypelagic waters. There was only a single transition to benthic lifestyle on the stem of *Rhodaliidae*.

>>>>

Siphonophores are abundant predators in the pelagic realm, ranging from the surface (*Physalia physalis*) to bathypelagic depths (Figure 4, S5) [@mapstone2014global]. While there are some pleustonic (*Physalia*) and benthic (*Rhodaliidae*) siphonophores, the phylogeny indicates that the siphonophore MRCA was probably planktonic, as most extant siphonophore taxa are. Some siphonophore species (such as *Bargmannia lata*) have been observed at abyssopelagic depths near 4000m. An interesting question that arises from these facts is what was the evolutionary history of siphonophore vertical habitat use of the water columns. Using the present phylogeny, we reconstructed the median depth changes along the phylogeny under a Brownian Motion model (Supplementary figure S5). This model indicates a mesopelagic common ancestor, with several independent transition events to epipelagic (light blue) and bathypelagic (dark blue) waters. This reconstruction only included species recorded using an ROV, thus it excludes many other independent colonizations of the epipelgic habitat. Species such as *Hippopodius hippopus*, *Athorybia rosacea*, *Diphyes dispar*, and *Chelophyes appendiculata* are often encountered blue water diving less than 20m from the surface (Figure 4). There was only a single transition to benthic lifestyle on the stem of *Rhodaliidae*, and a single transition to a pleustonic lifestyle in the stem of *Physalia physalis*. Further research should address whether these transitions are following evolutionary changes in feeding habits and prey availability.
